\documentclass{article}
\title{FPL bot}
\author{Sebastian Skjensvold}

\newcommand{\ra}{\rightarrow}
\newcommand{\sumn}{\sum_{k=1}^{n}}
\newcommand{\pb}{\pagebreak \\ \noindent}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{tikz-cd}
\usepackage{graphicx}
\begin{document}
	\maketitle
	\noindent
	\tableofcontents
	\pb
		\section{Code Structure}
		The general idea for the players is to define Player as a object with attributes; Team, Price, Position, and some undecided attributes of expected points (xp). We create subclasses for each position as there are restraints on the number of players of one position which could be in the team at the same time. The team we defined as a list 
		\begin{verbatim}
		team = [GK1, GK2, DEF1, DEF2, DEF3, DEF4, DEF5, MID1, MID2, MID3, MID4, MID5, FWD1, FWD2, FWD3]
		\end{verbatim}
		We then define a function to calculate the total price of the team, and a function to calculate the total expected points of the team. We also define a function to calculate the total expected points of the team, given a set of players. This is used to calculate the expected points of the team, given a set of players, and the rest of the team is filled with the best players. We also define a function to calculate the total price of the team, given a set of players. This is used to calculate the price of the team, given a set of players, and the rest of the team is filled with the cheapest players. We also define a function to calculate the total expected points of the team, given a set of players. This is used to calculate the expected points of the team, given a set of players, and the rest of the team is filled with the best players. We also define a function to calculate the total price of the team, given a set of players. This is used to calculate the price of the team, given a set of players, and the rest of the team is filled with the cheapest players. We also define a function to calculate the total expected points of the team, given a set of players. This is used to calculate the expected points of the team, given a set of players, and the rest of the team is filled with the best players. We also define a function to calculate the total price of the team, given a set of players. This is used to calculate the price of the team, given a set of players, and the rest of the team is filled with the cheapest players. We also define a function to calculate the total expected points of the team, given a set of players. This is used to calculate the expected points of the team, given a set of players, and the rest of the team is filled with the best players. We also define a function to calculate the total price of the team, given a set of players. This is used to calculate the price of the team, given a set of players, and the rest of the team is filled with the cheapest players. We also define a function to calculate the total expected points of the team, given a set of players. This is used to calculate the expected points of the team, given a set of players, and the rest of the team is filled with the best players. We also define a function to calculate the total price
\end{document}